---
title: "Trial Function"
author: "Stephen Schwartz"
date: "9/11/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## 1. Write a function to calculate the mean:
```{r}
HW3_mean <- function(datainput){
  finaloutput <- (sum(datainput) / length(datainput))
  return(finaloutput)
}
```

#Download this data set and use it for questions 2-4:
```{r}
install.packages("tidytuesdayR")

key_crop_yields <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-09-01/key_crop_yields.csv')

```


## 2. The range (first and last) of the variable Year.
```{r}
myrange <- range(key_crop_yields$Year, na.rm = TRUE)
myrange
```


## 3. Using the function from !3, calculate the mean of the variable "Maize (tonnes per hectare)".
```{r}
CornYieldnew <- key_crop_yields$`Maize (tonnes per hectare)`

CornYieldnarm <- CornYieldnew[!is.na(CornYieldnew)]

Cornmean <- HW3_mean(CornYieldnarm)
Cornmean
```


## 4. Save a file with the variable named "Entity"
```{r}
Entity <- key_crop_yields$Entity
write.table(Entity, file = "Entity.txt", sep = ",")
```



Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
